---
title: "Basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction
This document shows how to use SimpleSim to generate Guassian blobs to highlight how the package works. 


# Getting Started
The package is named SimpleSim and can be brought into your environment as: 
```{r setup}
library(SimpleSim)
```

Now we are ready to start using the functions. In what follows we will generate Gaussian blobs using the SimBlobs function. 


# Blobs
Blobs are Isotropic Gaussians with varying numbers of centers. To generate eight blobs on a 2d place, each with N samples we can do the following: 

```{r}
blobs = SimBlobs(100, nFeatures = 2)
plot(blobs$x[,1], blobs$x[,2], xlab = "x1", ylab = "x2", main = "2D Blobs")
```



The output of any SimpleSim function will be a list of simulated data. For blobs we get back x (a matrix whose rows represent observations), y (class labels for each blob) and centers (the centers for the generated blobs).

## Changing Centers
Below we play with some more features of the Blobs function.
```{r}
# specifying the centers of each blob.  
centers = matrix(c(2,3,10,11), byrow = T, ncol = 2)
blobs = SimBlobs(40, centers)
plot(blobs$x[,1], blobs$x[,2], xlab = "x1", ylab = "x2", main = "2D Blobs Centers Given")
```

## Changing Centers
We can create a matrix of centers (each row is a center).
```{r}
# specifying the centers of each blob.  
centers = matrix(c(2,3,10,11), byrow = T, ncol = 2)
blobs = SimBlobs(40, centers)
plot(blobs$x[,1], blobs$x[,2], xlab = "x1", ylab = "x2", main = "2D Blobs Centers Given")
```

## Changing Bounding Box
You can also choose to have the centers of the blobs we uniformly generated within the interval given by centerBox. 

```{r}
closeBlobs = SimBlobs(40, centerBox = c(-1,1))
farBlobs = SimBlobs(40, centerBox = c(-100, 100))
par(mfrow = c(1,2))
plot(closeBlobs$x[,1], closeBlobs$x[,2], xlab = "x1", ylab = "x2", main = "2D Blobs Close")
plot(farBlobs$x[,1], farBlobs$x[,2], xlab = "x1", ylab = "x2", main = "2D Blobs Far")
```


