---
title: "PolyChangePoint"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PolyChangePoint}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction
This document shows examples simulating data from a polynomial change point model. As always SimpleSim provides an easy solution!



# Two Linear Models

First we load the our package. 
```{r setup}
library(SimpleSim)
```

Now let's get to business. We want 100 observations from this model: 
$$y = 0.1 * x * I_{x<.5}  + 5 * x * I_{x\geq 0.5}$$
Where $I_x$ is the 'ol indicator function.


Now remember that the coefficients are placed in decreasing order, so for our first model we should have c(.1, 0).


```{r}
N = 100
linearResult = SimPolyChangePoint(N, sigma = 0.1, x0 = 0.5, m1 = c(.1, 0), m2 = c(5, 0))
plot(linearResult$data[,1], linearResult$data[,2], ylab = "y", xlab = "x", main = "Linear Change Point Model")
```
Now those are two lines! Be better if they have some curve to them though, so let's bump up the degree of the first model. 



# A Quadratic and Linear Model
Let's give the first model a little $x^2$ term and change the domain. So our model is:
$$y = (1.2 *x^2 + 0.1 * x) * I_{x<5}  + 5 * x * I_{x\geq 5}$$

```{r}
N = 100
linearResult = SimPolyChangePoint(N, sigma = 0.1, xRange = c(0, 10),x0 = 5, m1 = c(2, .1, 0), m2 = c(5, 0))
plot(linearResult$data[,1], linearResult$data[,2], ylab = "y", xlab = "x", main = "Linear Change Point Model")
```



# Discontinuity
That's a little cooler, but I hate that they meet at the change-point. Let's add a discontinuity and see how cool it is. 


```{r}
N = 100
linearResult = SimPolyChangePoint(N, sigma = 0.1, xRange = c(0, 10),x0 = 5, m1 = c(2, .1, 0), m2 = c(5, 15))
plot(linearResult$data[,1], linearResult$data[,2], ylab = "y", xlab = "x", main = "Linear Change Point Model")
```


Now that's a rollercoaster I'd be afraid to ride!

