---
title: "SwissRoll"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SwissRoll}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
This document goes through using the SimSwissRoll function.


# Swiss Roll Usage
As always start by loading SimpleSim
```{r setup}
library(SimpleSim)
```

Next we generate 1000 realizations from the Swiss Roll, and see what we get out. 

```{r}
swissResults = SimSwissRoll(1000, .1)
names(swissResults)
```
SimSwissRoll returns a list with the "data" and "t". The data is the x,y,z coordinates of each obersation and t is the value of t for that triple. We can plot the z vs. x and see our familiar treat. 

```{r}
data = swissResults$data
plot(data[,1], data[,3], ylab = "z", xlab = "x", main = "Swiss Roll z vs. x")
```

## A Noisy Swiss Roll
We can also make a noisier version of our favoriate pastry by changing the value of sigma. 
```{r}
swissResults = SimSwissRoll(1000, sigma = 2)
data = swissResults$data
plot(data[,1], data[,3], ylab = "z", xlab = "x", main = "Noisy Swiss Roll z vs. x")

```

That barely even looks like our favorite food! However, when you squint all is good. 